No Interaction on a Cost Grade

### 2022-12-06 graphs_newt_snakes/no_inter_cost_grade.Rmd
I created the interrate grade and snake grade file. I ran or re-ran all of the data to look at the correlation between phenotypes as well as other results. Next step I will spend more time exploring these results

---
title: "Interaction Grade"
output: html_document
date: '2022-12-06'
---

@@

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=interrate_grade
thefolder=${thepath}${foldername}/*

@@

interrate_grade_lit<- read.csv("~/Desktop/interrate_grade/all_lit.txt" , header = TRUE)

interrate_grade_lit$group_rep <- paste0(interrate_grade_lit$snake_mu_rate, "_", interrate_grade_lit$snake_mu_effect_sd,"_",interrate_grade_lit$newt_mu_rate, "_", interrate_grade_lit$newt_mu_effect_sd, "_", interrate_grade_lit$rep)

interrate_grade_lit$group <- paste0(interrate_grade_lit$snake_mu_rate, "_", interrate_grade_lit$snake_mu_effect_sd,"_",interrate_grade_lit$newt_mu_rate, "_", interrate_grade_lit$newt_mu_effect_sd)

interrate_grade_lit$sim=LETTERS[factor(interrate_grade_lit$group)]
interrate_grade_lit$dif <- interrate_grade_lit$Snake_mean_Pheno-interrate_grade_lit$Newt_mean_Pheno

interrate_grade_cor<- read.csv("~/Desktop/interrate_grade/all_cor.txt" , header = TRUE)
interrate_grade_cor$group_rep <- paste0(interrate_grade_cor$snake_mu_rate, "_", interrate_grade_cor$snake_mu_effect_sd,"_",interrate_grade_cor$newt_mu_rate, "_", interrate_grade_cor$newt_mu_effect_sd, "_", interrate_grade_cor$rep)
interrate_grade_cor$group <- paste0(interrate_grade_cor$snake_mu_rate, "_", interrate_grade_cor$snake_mu_effect_sd,"_",interrate_grade_cor$newt_mu_rate, "_", interrate_grade_cor$newt_mu_effect_sd)
interrate_grade_cor$sim=LETTERS[factor(interrate_grade_cor$group)]

@@

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=interrate_grade_lit
#cfile=interrate_grade_cor 
 # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

@@

two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file=interrate_grade_lit
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

@@

#two_hist_death_all_rep(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)

@@

### Phenotype differences 
```{r, graphing by gen}
trends_by_gen(interrate_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

#aggregate(interrate_grade_lit[which(interrate_grade_lit$generation>=100 & interrate_grade_lit$generation<=50000),]$dif, list(interrate_grade_lit[which(interrate_grade_lit$generation>=100 & interrate_grade_lit$generation<=50000),]$group_rep), FUN=mean)

@@

```{r, average difference}
aggregate(interrate_grade_lit[which(interrate_grade_lit$generation>=100 & interrate_grade_lit$generation<=50000),]$dif, list(interrate_grade_lit[which(interrate_grade_lit$generation>=100 & interrate_grade_lit$generation<=50000),]$group), FUN=mean) 
```

@@

whale_gen(interrate_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

@@

suppressMessages(print(two_hist(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

#suppressMessages(print(two_hist_all_rep(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))

@@

boxplot_cors_by_gen(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

#four_types_boxplot_cors_by_gen(interrate_grade_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

@@

### Plot 1
```{r, GA1 cor by dif windows}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

@@

```{r, GA1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(interrate_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

@@

### Random 1  
```{r, GA1 cor and pheno}
GA1_pattern <- unique(paste0(interrate_grade_lit$snake_mu_rate, "_", interrate_grade_lit$snake_mu_effect_sd,"_",interrate_grade_lit$newt_mu_rate, "_", interrate_grade_lit$newt_mu_effect_sd, "_", interrate_grade_lit$rep))

@@

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(interrate_grade_lit, interrate_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(interrate_grade_lit, interrate_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

@@

cor_trends_by_gen(interrate_grade_lit, interrate_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

@@

cor_trends_by_gen(interrate_grade_lit, interrate_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

@@

# for(i in 1:length(unique(interrate_grade_lit$rep))){
#   myine<-whale_gen(interrate_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(interrate_grade_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(interrate_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(interrate_grade_lit$rep)[1])
```

@@

# for(i in 1:length(unique(interrate_grade_lit$rep))){
#   myine<-two_hist(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(interrate_grade_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(interrate_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(interrate_grade_lit$rep)[1] )

@@

min_gen=100
max_gen=5000
GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

@@

# summary
GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

@@

# summary
GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

@@

GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

@@

GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

@@

### Late Difference Summary
```{r, dif plots summary 3}
min_gen=45000
max_gen=50000
GA_summary(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

@@

GA_summary_by_species(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

@@

GA_summary_by_species(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

@@

min_gen=100
max_gen=5000
#heatmap
build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)  
```{r, early plots Heatmap 2}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

@@

### Population Size (Late) 
```{r, early plots Heatmap 3}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early) 
```{r, early plots Heatmap pheno 1}
min_gen=100
max_gen=5000
build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

@@

build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

@@

build_heatmap(interrate_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)

>>>>

---
title: "No Interaction on a Cost Grade"
output: html_document
date: '2022-12-06'
---

@@

# Run these comands while in The the folder that contains the file you would like to condence
# Goal is to condence all the text files into one file 
# Requirements: need to have the same name and need to add additional columns
thepath=/Users/victoria/Desktop/
foldername=no_interaction_cost_grade
thefolder=${thepath}${foldername}/*

@@

no_interaction_cost_grade_lit<- read.csv("~/Desktop/no_interaction_cost_grade/all_lit.txt" , header = TRUE)

no_interaction_cost_grade_lit$group_rep <- paste0(no_interaction_cost_grade_lit$snake_mu_rate, "_", no_interaction_cost_grade_lit$snake_mu_effect_sd,"_",no_interaction_cost_grade_lit$newt_mu_rate, "_", no_interaction_cost_grade_lit$newt_mu_effect_sd, "_", no_interaction_cost_grade_lit$rep)

no_interaction_cost_grade_lit$group <- paste0(no_interaction_cost_grade_lit$snake_mu_rate, "_", no_interaction_cost_grade_lit$snake_mu_effect_sd,"_",no_interaction_cost_grade_lit$newt_mu_rate, "_", no_interaction_cost_grade_lit$newt_mu_effect_sd)

no_interaction_cost_grade_lit$sim=LETTERS[factor(no_interaction_cost_grade_lit$group)]
no_interaction_cost_grade_lit$dif <- no_interaction_cost_grade_lit$Snake_mean_Pheno-no_interaction_cost_grade_lit$Newt_mean_Pheno

no_interaction_cost_grade_cor<- read.csv("~/Desktop/no_interaction_cost_grade/all_cor.txt" , header = TRUE)
no_interaction_cost_grade_cor$group_rep <- paste0(no_interaction_cost_grade_cor$snake_mu_rate, "_", no_interaction_cost_grade_cor$snake_mu_effect_sd,"_",no_interaction_cost_grade_cor$newt_mu_rate, "_", no_interaction_cost_grade_cor$newt_mu_effect_sd, "_", no_interaction_cost_grade_cor$rep)
no_interaction_cost_grade_cor$group <- paste0(no_interaction_cost_grade_cor$snake_mu_rate, "_", no_interaction_cost_grade_cor$snake_mu_effect_sd,"_",no_interaction_cost_grade_cor$newt_mu_rate, "_", no_interaction_cost_grade_cor$newt_mu_effect_sd)
no_interaction_cost_grade_cor$sim=LETTERS[factor(no_interaction_cost_grade_cor$group)]

@@

cor_trends_by_gen <- function(file, cfile, title, subt, x_label, x_label_cor, y_label, min_gen, max_gen, pattern){
#file=no_interaction_cost_grade_lit
#cfile=no_interaction_cost_grade_cor 
 # pattern="1.0e-10_0.05_1.0e-08_0.005_3"
 file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd,"_", file$rep)
  cfile$snake_newt_rep <- paste0(cfile$snake_mu_rate, "_", cfile$snake_mu_effect_sd, "_", cfile$newt_mu_rate, "_", cfile$newt_mu_effect_sd, "_", cfile$rep)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen & file$snake_newt_rep==pattern),]) +
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
      ggtitle(title, subtitle = paste0(subt," pattern ", pattern, " From ", min_gen, " gen to ", max_gen, " gen"))+
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #ylim(0,10)+
    #xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred"),
labels = c("Snake", "Newt"))+
    theme_bw() +theme(legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      plot.margin=unit(c(1,1,+0.3,1), "cm"))

@@

two_hist_death_all_rep <- function(file, title, subt, x_label, y_label,min_gen, max_gen){
  #file=no_interaction_cost_grade_lit
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)

@@

#two_hist_death_all_rep(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=20000, max_gen=25000)

@@

### Phenotype differences 
```{r, graphing by gen}
trends_by_gen(no_interaction_cost_grade_lit, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=1)

#aggregate(no_interaction_cost_grade_lit[which(no_interaction_cost_grade_lit$generation>=100 & no_interaction_cost_grade_lit$generation<=50000),]$dif, list(no_interaction_cost_grade_lit[which(no_interaction_cost_grade_lit$generation>=100 & no_interaction_cost_grade_lit$generation<=50000),]$group_rep), FUN=mean)

@@

```{r, average difference}
aggregate(no_interaction_cost_grade_lit[which(no_interaction_cost_grade_lit$generation>=100 & no_interaction_cost_grade_lit$generation<=50000),]$dif, list(no_interaction_cost_grade_lit[which(no_interaction_cost_grade_lit$generation>=100 & no_interaction_cost_grade_lit$generation<=50000),]$group), FUN=mean) 
```

@@

whale_gen(no_interaction_cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

@@

suppressMessages(print(two_hist(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

#suppressMessages(print(two_hist_all_rep(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/100 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen)))

@@

boxplot_cors_by_gen(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation Trials", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

#four_types_boxplot_cors_by_gen(no_interaction_cost_grade_cor, "Simulation four Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)

@@

### Plot 1
```{r, GA1 cor by dif windows}
ginmin = 0
ginmax = 5000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

@@

```{r, GA1 cor by dif windows 2}
ginmin = 5000
ginmax = 10000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 3
```{r, GA1 cor by dif windows 3}
ginmin = 10000
ginmax = 15000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 4
```{r, GA1 cor by dif windows 4}
ginmin = 15000
ginmax = 20000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 5
```{r, GA1 cor by dif windows 5}
ginmin = 20000
ginmax = 25000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 6
```{r, GA1 cor by dif windows 6}
ginmin = 25000
ginmax = 30000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 7
```{r, GA1 cor by dif windows 7}
ginmin = 30000
ginmax = 35000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 8
```{r, GA1 cor by dif windows 8}
ginmin = 35000
ginmax = 40000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 9
```{r, GA1 cor by dif windows 9}
ginmin = 40000
ginmax = 45000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

### Plot 10
```{r, GA1 cor by dif windows 10}
ginmin = 45000
ginmax = 50000
suppressMessages(print(hist_cors_by_gen_col_rep(no_interaction_cost_grade_cor, "Simulation Correlation Comparied to Real Correlation", "GA1", "newt/snake GAs&rep", "Cor", ginmin, ginmax)))
```

@@

### Random 1  
```{r, GA1 cor and pheno}
GA1_pattern <- unique(paste0(no_interaction_cost_grade_lit$snake_mu_rate, "_", no_interaction_cost_grade_lit$snake_mu_effect_sd,"_",no_interaction_cost_grade_lit$newt_mu_rate, "_", no_interaction_cost_grade_lit$newt_mu_effect_sd, "_", no_interaction_cost_grade_lit$rep))

@@

# for(i in myrandomlist){
#   myine<-cor_trends_by_gen(no_interaction_cost_grade_lit, no_interaction_cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[i])
#   plot(myine)
# }

cor_trends_by_gen(no_interaction_cost_grade_lit, no_interaction_cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[1]])

@@

cor_trends_by_gen(no_interaction_cost_grade_lit, no_interaction_cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[2]])
```

@@

cor_trends_by_gen(no_interaction_cost_grade_lit, no_interaction_cost_grade_cor, "test", "GA1", "newt/snake GAs&rep","other", "Cor", min_gen=100, max_gen=50000, pattern=GA1_pattern[myrandomlist[3]])
```

@@

# for(i in 1:length(unique(no_interaction_cost_grade_lit$rep))){
#   myine<-whale_gen(no_interaction_cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_interaction_cost_grade_lit$rep)[i])
#   plot(myine)
# 
# }
whale_gen(no_interaction_cost_grade_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize", min_gen=min_gen, max_gen=max_gen, rep=unique(no_interaction_cost_grade_lit$rep)[1])
```

@@

# for(i in 1:length(unique(no_interaction_cost_grade_lit$rep))){
#   myine<-two_hist(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_interaction_cost_grade_lit$rep)[i] )
#   suppressMessages(plot(myine))
# }

two_hist(no_interaction_cost_grade_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Phenotype (purple) & Snake-Newt Popsize/100 (green)",  min_gen=min_gen, max_gen=max_gen, rep=unique(no_interaction_cost_grade_lit$rep)[1] )

@@

min_gen=100
max_gen=5000
GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

@@

# summary
GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")
```

@@

# summary
GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="Newt_pop_size", y_line="Snake_pop_size", title="Space: Newt VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Popsize")

@@

GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")
```

@@

GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

@@

### Late Difference Summary
```{r, dif plots summary 3}
min_gen=45000
max_gen=50000
GA_summary(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="Snake_pop_size", title="Space: Dif VS Snake Population Size", subt="Gen 16sims", y_label="Snake Popsize", x_label="Dif")

@@

GA_summary_by_species(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="snake", title="Space: Dif VS Snake GA", subt="Gen 16sims", y_label="Snake GA", x_label="Dif")

@@

GA_summary_by_species(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, x_line="dif", y_line="newt", title="Space: Dif VS Newt GA", subt="Gen 16sims", y_label="Newt GA", x_label="Dif")

@@

min_gen=100
max_gen=5000
#heatmap
build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Population Size (Mid)  
```{r, early plots Heatmap 2}
min_gen=25000
max_gen=30000
#heatmap
build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)

@@

### Population Size (Late) 
```{r, early plots Heatmap 3}
min_gen=45000
max_gen=50000
#heatmap
build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="Snake_pop_size", fill_line_text="Snake Population Size", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA", red_blue=F)
```

### Phenotype (Early) 
```{r, early plots Heatmap pheno 1}
min_gen=100
max_gen=5000
build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

@@

build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
```

@@

build_heatmap(no_interaction_cost_grade_lit, min_gen=min_gen, max_gen=max_gen, fill_line="dif", fill_line_text="Snake-Newt", title="Newt GA by Snake GA", subt="16 Sim Heatmap", y_label="Snake GA", x_label="Newt GA",red_blue=T)
